Expert-In-The-Loop Causal Discovery: Iterative Model Refinement Using Expert Knowledge

### 2025-01-30 paper/main.tex
Fixes
Updates

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{fancyvrb}
% \usepackage[ruled]{algorithm2e}

@@

\begin{figure}
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=1]{figures.pdf}
	\caption{PC algorithm $ \chi^2 $ test. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=2]{figures.pdf}
	\caption{PC algorithm $ \chi^2 $ test. $ N=800$ }
\end{subfigure}
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=5]{figures.pdf}
	\caption{Hill Climb Search BIC Score. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
	\includegraphics[page=6]{figures.pdf}
	\caption{Hill Climb Search BIC Score. $ N=800$ }
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=3]{figures.pdf}
	\caption{PC algorithm residualization test. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
	\includegraphics[page=4]{figures.pdf}
	\caption{PC algorithm residualization test. $ N=800$ }
\end{subfigure}
\end{subfigure}

@@

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{todonotes}
\usepackage{bm}
\usepackage{subcaption}
\usepackage{fancyvrb}
\usepackage[ruled]{algorithm2e}

@@

\begin{figure}
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=1]{figures.pdf}
	\caption{PC algorithm $ \chi^2 $ test. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=2]{figures.pdf}
	\caption{PC algorithm $ \chi^2 $ test. $ N=800$ }
\end{subfigure}
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=5]{figures.pdf}
	\caption{Hill Climb Search BIC Score. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
	\includegraphics[page=6]{figures.pdf}
	\caption{Hill Climb Search BIC Score. $ N=800$ }
\end{subfigure}
\begin{subfigure}{0.25 \textwidth}
	\includegraphics[page=3]{figures.pdf}
	\caption{PC algorithm residualization test. $ N=400$ }
\end{subfigure}%
\begin{subfigure}{0.25\textwidth}
	\includegraphics[page=4]{figures.pdf}
	\caption{PC algorithm residualization test. $ N=800$ }
\end{subfigure}

@@

\begin{verbatim}
	Input: Dataset $ D $ on variables $ \bm{X} $
	Output: Learned DAG G.

	function compute_effects(G):
		pvalues <- dict()
		effects <- dict()
		for X_i, X_j in X:
			if edge between X_i, X_j:
				p_values[(X_i, X_j)] <- pvalue(X_i, X_j, pa_{\bar{G}}(X_i) \cup pa_{\bar{G}}(X_j))
				effects[(X_i, X_j)] <- \phi(X_i, X_j, pa_{\bar{G}}(X_i) \cup pa_{\bar{G}}(X_j))
			else:
				p_values[(X_i, X_j)] <- pvalue(X_i, X_j, pa_{\bar{G}}(X_i) \cup pa_{\bar{G}}(X_j))
				effects[(X_i, X_j)] <- \phi(X_i, X_j, pa_{\bar{G}}(X_i) \cup pa_{\bar{G}}(X_j))
		return p_values, effects

	$ G $ <- Empty Graph
	p_values, effects <- compute_effects(G)

\end{verbatim}

\begin{algorithm}
	\KwData{Data set $ D $ on variables $ \bm{X} $, pthres, effectthres}
	\KwResult{The learned DAG: $ G $}
	\BlankLine
	$ G \leftarrow $ Empty Graph
\end{algorithm}
